\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
benchmark tabular results

\documentclass{article}
\usepackage{fullpage}
%\usepackage{times}
\usepackage{url}
\usepackage{amsmath,amsthm,amssymb,color}
%\usepackage{multicol}
\usepackage{float}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{courier}
\usepackage{listings}
%\usepackage[all]{hypcap}

@@

\section{Evaluation}
%% XXX: TODO

>>>>

\documentclass{article}
\usepackage{fullpage}
%\usepackage{times}
\usepackage{url}
\usepackage{amsmath,amsthm,amssymb,color}
%\usepackage{multicol}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{courier}
\usepackage{listings}
%\usepackage[all]{hypcap}

@@

\section{Evaluation}
To evaluate our work, we tested for correctness using Mozilla's large
repository of regression tests, and measured the impact of our
optimization by the commonly available benchmark suites.
%% TODO : elim stats too

There are three benchmark suites which are generally used to measure Javascript
JIT compilers: the v8bench suite developed by Google, the SunSpider benchmark
suite developed by Apple, and the Kraken benchmark suite developed by Mozilla.

We ran each benchmark suite on IonMonkey, both with and without our range
analysis pass, and measured the performance differences. The results are
summarized below:

\begin{figure}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:            &   -                & 3414.7ms $\pm$ 0.5\% &  3397.4ms $\pm$ 0.2\% & \\
\hline
\hline  crypto:       &   -                &  104.8ms $\pm$ 0.7\% &   104.7ms $\pm$ 0.4\% & \\
\hline  deltablue:    &   -                &  206.7ms $\pm$ 0.4\% &   205.8ms $\pm$ 0.4\% & \\
\hline  earley-boyer: &   1.009x as fast   & 1817.8ms $\pm$ 0.8\% &  1801.5ms $\pm$ 0.3\% &     significant \\
\hline  raytrace:     &   -                &  585.9ms $\pm$ 0.5\% &   584.8ms $\pm$ 0.3\% & \\
\hline  regexp:       &   -                &  492.9ms $\pm$ 0.6\% &   491.7ms $\pm$ 0.1\% & \\
\hline  richards:     &   1.018x as slow   &  149.0ms $\pm$ 0.7\% &   151.7ms $\pm$ 0.3\% &     significant \\
\hline  splay:        &   -                &   57.5ms $\pm$ 0.8\% &    57.1ms $\pm$ 0.6\% & \\
\hline
\end{tabular}
\caption{v8bench benchmark results}
\label{fig:v8bench}
\end{figure}

\begin{figure}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}                   & \textbf{Comparison}       &     \textbf{From}         &        \textbf{To}           &  \textbf{Details} \\
\hline\hline
Total:                 & 1.001x as slow & 279.2ms $\pm$ 0.1\% &  279.6ms $\pm$ 0.1\%   &  significant \\
\hline\hline
3d:                  & 1.004x as slow &  52.5ms $\pm$ 0.3\% &   52.7ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} cube:              & ??               &  25.1ms $\pm$ 0.3\% &   25.2ms $\pm$ 0.4\%   &  \textit{might} be 1.001x as slow \\
\hline\hspace{1em} morph:             & ??               &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.003x as slow \\
\hline\hspace{1em} raytrace:          & 1.009x as slow &  20.4ms $\pm$ 0.5\% &   20.6ms $\pm$ 0.4\%   &  significant \\
\hline\hline
access:              & 1.011x as fast   &  18.5ms $\pm$ 0.3\% &   18.3ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} binary-trees:      & 1.019x as slow &   3.0ms $\pm$ 0.9\% &    3.0ms $\pm$ 0.9\%   &  significant \\
\hline\hspace{1em} fannkuch:          & 1.034x as fast   &   8.8ms $\pm$ 0.3\% &    8.5ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} nbody:             & 1.035x as fast   &   3.6ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} nsieve:            & 1.052x as slow &   3.1ms $\pm$ 0.6\% &    3.3ms $\pm$ 0.5\%   &  significant \\
\hline\hline
bitops:              & 1.008x as fast   &  11.4ms $\pm$ 0.4\% &   11.3ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} 3bit-bits-in-byte: & 1.009x as fast   &   1.0ms $\pm$ 0.6\% &    1.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} bits-in-byte:      & 1.023x as fast   &   4.1ms $\pm$ 0.5\% &    4.0ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} bitwise-and:       & ??               &   2.8ms $\pm$ 0.5\% &    2.8ms $\pm$ 0.6\%   &  \textit{might} be 1.005x as slow \\
\hline\hspace{1em} nsieve-bits:       & -                &   3.6ms $\pm$ 0.5\% &    3.6ms $\pm$ 0.5\% & \\
\hline\hline
controlflow:         & 1.020x as slow &   2.3ms $\pm$ 0.7\% &    2.3ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} recursive:         & 1.020x as slow &   2.3ms $\pm$ 0.7\% &    2.3ms $\pm$ 0.4\%   &  significant \\
\hline\hline
crypto:              & 1.008x as slow &  27.3ms $\pm$ 0.3\% &   27.5ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} aes:               & 1.009x as slow &  15.5ms $\pm$ 0.4\% &   15.6ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} md5:               & ??               &   6.9ms $\pm$ 0.7\% &    6.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{1em} sha1:              & 1.008x as slow &   4.9ms $\pm$ 0.5\% &    4.9ms $\pm$ 0.5\%   &  significant \\
\hline\hline
date:                & 1.008x as fast   &  62.6ms $\pm$ 0.2\% &   62.1ms $\pm$ 0.2\%   &  significant \\
\hline\hspace{1em} format-tofte:      & -                &  42.6ms $\pm$ 0.2\% &   42.6ms $\pm$ 0.2\%   & \\
\hline\hspace{1em} format-xparb:      & 1.023x as fast   &  20.0ms $\pm$ 0.3\% &   19.5ms $\pm$ 0.3\%   &  significant \\
\hline\hline
math:                & ??               &  13.2ms $\pm$ 0.3\% &   13.2ms $\pm$ 0.4\%   &  \textit{might} be 1.003x as slow \\
\hline\hspace{1em} cordic:            & 1.021x as fast   &   2.7ms $\pm$ 0.4\% &    2.6ms $\pm$ 0.6\%   &  significant \\
\hline\hspace{1em} partial-sums:      & -                &   7.1ms $\pm$ 0.5\% &    7.1ms $\pm$ 0.6\% & \\
\hline\hspace{1em} spectral-norm:     & 1.024x as slow &   3.4ms $\pm$ 0.6\% &    3.5ms $\pm$ 0.4\%   &  significant \\
\hline\hline
regexp:              & 1.012x as fast   &  10.2ms $\pm$ 0.5\% &   10.0ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} dna:               & 1.012x as fast   &  10.2ms $\pm$ 0.5\% &   10.0ms $\pm$ 0.4\%   &  significant \\
\hline\hline
string:              & 1.009x as slow &  81.3ms $\pm$ 0.2\% &   82.1ms $\pm$ 0.2\%   &  significant \\
\hline\hspace{1em} base64:            & ??               &   4.9ms $\pm$ 0.6\% &    4.9ms $\pm$ 0.4\%   &  \textit{might} be 1.006x as slow \\
\hline\hspace{1em} fasta:             & 1.012x as slow &   6.9ms $\pm$ 0.5\% &    6.9ms $\pm$ 0.4\%   &  significant \\
\hline\hspace{1em} tagcloud:          & -                &  23.2ms $\pm$ 0.4\% &   23.3ms $\pm$ 0.3\% & \\
\hline\hspace{1em} unpack-code:       & 1.014x as slow &  39.5ms $\pm$ 0.2\% &   40.1ms $\pm$ 0.3\%   &  significant \\
\hline\hspace{1em} validate-input:    & 1.007x as slow &   6.8ms $\pm$ 0.4\% &    6.9ms $\pm$ 0.5\%   &  significant  \\
\hline
\end{tabular}
\caption{SunSpider benchmark results}
\label{fig:sunspider}
\end{figure}

\begin{figure}[H]
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:                      & 1.015x as fast   & 2319.6ms $\pm$ 0.3\% &  2285.4ms $\pm$ 0.4\%  &   significant\\
\hline\hline
      ai:                       & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hspace{1em} astar:                  & 1.118x as fast   &  121.3ms $\pm$ 0.8\% &   108.5ms $\pm$ 1.2\%  &   significant\\
\hline\hline
      audio:                    & -                &  842.8ms $\pm$ 0.4\% &   838.0ms $\pm$ 0.7\%  &\\
\hline\hspace{1em} beat-detection:         & ??               &  393.0ms $\pm$ 1.0\% &   397.6ms $\pm$ 1.5\%  &   \textit{might} be 1.012x as slow\\
\hline\hspace{1em} dft:                    & 1.030x as fast   &  162.6ms $\pm$ 0.6\% &   157.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{1em} fft:                    & 1.016x as fast   &  123.5ms $\pm$ 0.2\% &   121.6ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} oscillator:             & 1.017x as fast   &  163.7ms $\pm$ 0.3\% &   160.9ms $\pm$ 0.3\%  &   significant\\
\hline\hline
      imaging:                  & 1.020x as fast   &  569.1ms $\pm$ 0.9\% &   557.9ms $\pm$ 1.3\%  &   significant\\
\hline\hspace{1em} gaussian-blur:          & -                &  197.2ms $\pm$ 1.7\% &   193.7ms $\pm$ 2.1\%  &\\
\hline\hspace{1em} darkroom:               & -                &  248.2ms $\pm$ 0.3\% &   247.6ms $\pm$ 0.4\%  &\\
\hline\hspace{1em} desaturate:             & 1.062x as fast   &  123.8ms $\pm$ 3.2\% &   116.7ms $\pm$ 5.1\%  &   significant\\
\hline\hline
      json:                     & 1.019x as fast   &  121.3ms $\pm$ 0.2\% &   119.0ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} parse-financial:        & 1.005x as fast   &   75.8ms $\pm$ 0.2\% &    75.5ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} stringify-tinderbox:    & 1.044x as fast   &   45.5ms $\pm$ 0.5\% &    43.5ms $\pm$ 0.8\%  &   significant\\
\hline\hline
      stanford:                 & -                &  665.0ms $\pm$ 0.5\% &   662.2ms $\pm$ 0.4\%  &\\
\hline\hspace{1em} crypto-aes:             & -                &  160.7ms $\pm$ 1.5\% &   160.6ms $\pm$ 1.1\%  &\\
\hline\hspace{1em} crypto-ccm:             & 1.008x as slow &  158.6ms $\pm$ 0.4\% &   159.8ms $\pm$ 0.5\%  &   significant\\
\hline\hspace{1em} crypto-pbkdf2:          & 1.006x as fast   &  254.9ms $\pm$ 0.5\% &   253.3ms $\pm$ 0.4\%  &   significant\\
\hline\hspace{1em} crypto-sha256-iterative:& 1.025x as fast   &   90.8ms $\pm$ 0.4\% &    88.5ms $\pm$ 0.5\%  &   significant \\
\hline
\end{tabular}
\caption{Kraken benchmark results}
\label{fig:kraken}
\end{figure}
%% XXX: TODO
